Ecological network control

### 2018-05-22 paper/supp-info.Rmd
Figure all maximum matchings in supp info
Add figure example network

>>>>

```{r}
drake::loadd(fig_all_matching)
```

```{r fig-all-maximum-matching, fig.height=fig_all_matching$height, fig.width=fig_all_matching$width,fig.cap = "Finding a maximum matching in a complex network. (left) Directed network that indicate the direction of control between species. (center) Alternative bipartite representations of the directed networks. (right) The matchings in the bipartite representation mapped back to the original network."}
replayPlot(fig_all_matching$plot)
```

```{r}
drake::loadd(fig_small_network)
```

```{r fig-small-network, fig.height=fig_small_network$height, fig.width=fig_small_network$width,fig.cap = "**Illustration of the procedure with an empirical network**. (a) The initial visitation network. (b) The directed network in which the direction of control is determined based on the mutual dependences and asymmetries. (c) One of the possible maximum matchings calculated using the procedures illustrated in the Figures \\@ref(fig:fig-direction-of-control) and \\@ref(fig:fig-finding-all-matchings)"}
replayPlot(fig_small_network$plot)
```
